The `geomnet` package

### 2020-11-20 README.Rmd
upload new hex sticker!

---
title: "The `geomnet` package"
author: Sam Tyner, Heike Hofmann
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN Status](http://www.r-pkg.org/badges/version/geomnet)](https://cran.r-project.org/package=geomnet)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/geomnet)](http://www.r-pkg.org/pkg/geomnet)
[![Travis-CI Build Status](https://travis-ci.org/sctyner/geomnet.svg?branch=master)](https://travis-ci.org/sctyner/geomnet)

>>>>

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# geomnet <img src="man/figures/logo.png" align="right" width="120" />

[![CRAN Status](http://www.r-pkg.org/badges/version/geomnet)](https://cran.r-project.org/package=geomnet)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/geomnet)](https://www.r-pkg.org/pkg/geomnet)
[![Travis-CI Build Status](https://travis-ci.org/sctyner/geomnet.svg?branch=master)](https://travis-ci.org/sctyner/geomnet)
